---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# zkgr

<!-- badges: start -->
`r lifecycle::badge("experimental")`
<!-- badges: end -->

The goal of `zkgr` (pronounced "DBHDS packager") is to provide a template 
for R packages and documentation standardized across the Virginia Department of 
Behavioral Health and Developmental Services (DBHDS).  
  
This package provides 
the resources necessary to rapidly develop R packages that are aligned to DBHDS 
styles and policies.  


## Installation

To install this package, complete the steps below:  

1. Access the DBHDS Azure DevOps instance in a modern Web browser  
2. Navigate to the `zkgr` repository  
3. Copy the clone URL for the repository  
4. Using GitHub Desktop, clone from URL  
5. Open the `.Rproj` file in RStudio
6. Run `devtools::install()`
7. Restart R

TODO: Update this section to reflect use of `remotes::install_git()` with local 
copies of the relevant repositories. It appears as though the 
`devtools::install()` function, at least with the relevant defaults, does not 
install the package in the proper `base::.libPaths()` due to the use of the `package?renv` 
package.

## Using `zkgr`

Once you have successfully installed the `zkgr` package, you can use it 
to style your own R package.  
  
### Prerequisite: Knowledge of Package Development
If you are creating your own R package for the first time, it is highly 
recommended that you read [R Packages](https://r-pkgs.org/) by 
[Hadley Wickham](http://hadley.nz/) and [Jenny Bryan](http://jennybryan.org/) 
to gain some familiarity with this process before continuing. Reading 
*R Packages* will introduce you to the basic workflow 
involved in building an R package. More importantly for present purposes, 
*R Packages* will orient you to modern tools for developing 
R packages including [devtools](https://devtools.r-lib.org/), 
[usethis](https://usethis.r-lib.org/), and 
[pkgdown](https://pkgdown.r-lib.org/index.html).  
  
If you are interested in learning more about developing R packages, you can find 
additional resources in the following vignette: 
`vignette("additional-resources")`.  
  
### A Basic Example
  

```{r load, eval=FALSE}
# call this function within your package's project directory
library(devtools)
zkgr::use_pkgr(copyright_holder = "Office of Epidemiology and Health Analytics")
```

<!--
You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.
-->  

## Maintaining this Package  
This package is maintained by [`r zkgr:::get_maintainer_name()`](mailto: `r zkgr:::get_maintainer_email()`), 
but anyone with access to this [Git repository](https://dev.azure.com/dbhds-virginia/EHA%20Packages/_git/zkgr) 
can contribute by creating a branch, making changes, and submitting a pull 
request for the main branch.  
  
This package includes the function `zkgr::update_docs()` to facilitate 
updates to its installed documentation stored in `inst/pkgdown_docs/`. **This 
function is not exported for use in scripts or packages.**
