---
title: "How to use zkgr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to use zkgr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Working with `devtools` and `usethis`   
  
- `devtools` and `usethis` are R packages that expedite the development of R 
packages through user interaction  
- These packages can require some configuration. The `usethis` package includes 
a very helpful vignette entitled 
[usethis setup](https://usethis.r-lib.org/articles/usethis-setup.html)  
- Some useful functions/options:  
  - `usethis` provides *a lot* of output to the R console. This can be incredibly 
  useful as you work through developing a new package from scratch. Over time, 
  however, this can be annoying -- especially in the context of automated 
  testing with `testthat`. These messages can be silenced by setting 
  `options(usethis.quiet = TRUE)`. Within automated   tests, this can be set 
  using `withr::local_options(list(usethis.quiet = TRUE))`.  
  

## Steps  
  
### If using in an existing R package...  

1. Open the package root directory  
2. If an `.Rproj` file already exists, open the project in RStudio. If no such 
file exists, create one using the File > New Project... option  
3. Load packages  
```{r setup, eval=FALSE}
library(devtools)    # also loads `usethis` and sets .Rproj as active project
library(zkgr)
```
4. Adopt all `zkgr` default options at once
```{r use_pkgr, eval=FALSE}
use_pkgr()
```

